A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-14 manuscript/submission_MEE_2018.tex
working on reply

\section*{Abstract}
  [[was fine? Maybe lightly edit to make clear we're not doing a review]]
  \begin{enumerate}

@@

    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}. Identifying these interactions is a crucial step towards understanding (and predicting) the effects that species have on each other and the response of the community as a whole to external perturbations~\citep{Bartomeus2016,Giron2018}. Importantly, information is conveyed both by the presence and \emph{absence} of links between species. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    [[These two paragraphs try to frame our study more clearly]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.

    Here we introduce a simple Bayesian framework that can easily be adapted to different systems. First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomeus2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

    % Development of molecular sampling methods such as DNA barcoding hold great potential for uncovering interactions missed by other sampling methods (such as visit surveys)~\citep{Giron2018}, but these novel methods are also somewhat error-prone at present~\citep{}.

    % Accounting for differences in feasible (binary) interactions across life stages changes network structure~\citep{Clegg2018}.

    % Representing an ecological community as a network summarises both species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    % The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Worse, variability in community composition and interactions may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015} or individual preferences~\citep{Fodrie2015}.

    % Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012,Bartomeus,others}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    % Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling. [[cite previous attempts]] Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

    % In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths. To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred (assuming we can correctly identify the species involved), but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Did they interact?" and "Did we observe the interaction?" (Fig.~\ref{conceptual_fig}).

        \subsubsection*{Could the species interact?}

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}}) = \lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda_{ij}$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.

          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

        \subsubsection*{Did the species interact during sampling?}

          Assuming that an interaction is feasible (i.e., $L_{ij} = 1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij} = 1) = \chi_{ij}$. It is unlikely that $\chi_{ij} = 1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi_{ij} < 1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models. Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.

         % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks. For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby attempted to separate detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), which would require multi-year sampling efforts, or very rare interactions which would require extremely high sampling effort to detect. Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is high enough to ensure that all species present have been observed~\citep{Poisot2012,Jordano2016}.

          \textbf{Forbidden links}

            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

        \subsubsection*{Did we observe all interactions that occurred?}

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L_{ij} = 1$ and $X_{ij} = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D_{ij}|X_{ij} = 1,L_{ij} = 1)=\delta_{ij}$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce. For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.

          Some types of interactions will have higher detection uncertainty than others. Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species. Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}. If these infected individuals do not happen to be included in a sample, their interactions will be missed. Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.

    \subsection*{Can't we just sample more?}

        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between species $i$ and $j$, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}. Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}. Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.

        In short, high-quality sampling is an essential component of ecological network construction and increasing sampling (length of time, number of sites, number of distinct methods, etc.) can reduce some of the uncertainty about unobserved interactions. We believe, however, that empirical researchers generally sample to the maximum extent possible given constraints of time, resources, and study sites. This practical constraint means that reducing one source of uncertainty is likely to increase another source (e.g., sampling intensively at a single site may reduce detection uncertainty but will increase uncertainty due to variation between sites). The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}. For pairs of species with fewer observations, we can reduce uncertainty by combining the observed data available with prior knowledge about the system. This is straightforward to do using a Bayesian approach, as detailed below.

@@

    % Maybe we can move much of this to the Box and satisfy reviewer 1

    % We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed. For interactions which have been observed, methods already exist to quantify the probability of the interaction.

    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda_{ij}$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda_{ij}$ is:

    %     \begin{equation}
    %       \lambda_{MLE} = \frac{k}{n}  .
    %       \label{theta_MLE}
    %     \end{equation}

    % Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X_{ij} = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

    % To properly interpret $\lambda_{ij}$, we need to estimate the variance as well as the MLE. The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda_{ij}$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda_{ij}$. It is, however, straightforward to compute the confidence interval for the MLE of $\lambda_{ij}$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).

    % All of the above methods for estimating the variance of $\lambda_{ij}$ include the number of samples $n$. This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda_{ij}$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda_{ij}$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij} = \frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for a probability such as $\lambda_{ij}$ is the beta distribution:

>>>>

\section*{Abstract}

  \begin{enumerate}

@@

    Representing an ecological community as a network summarises both species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are usually limited to static representations of the communities they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Worse, variability in community composition and interactions may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or because of individual preferences~\citep{Fodrie2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling. Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths. To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. The detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).

        \subsubsection*{Interaction uncertainty}

          First, and most fundamentally, a pair of species may or may not have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur. In such cases, $\lambda = 0$ and there is no uncertainty.

          Most species pairs, however, do not have traits that absolutely prevent an interaction. This means that it is generally unclear whether an unobserved interaction is impossible or simply a rare phenomenon with $\lambda>0$. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}. Some interaction uncertainty is therefore inevitable.

        \subsubsection*{Process uncertainty}

         Even a feasible interaction, i.e. $L=1$, still may not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat. We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). In the field, however, process uncertainty is likely inevitable.

         One proposed solution to the problem of process uncertainty is to use repeated sampling of networks. For example,~\citet{Weinstein2017} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty. While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days. Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.

        \subsubsection*{Detection uncertainty}

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). The absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Because we cannot separate these possibilities, repeated sampling fails to satisfactorily address the uncertainty inherent in empirical networks.

    \subsection*{Estimating detection and process uncertainty}

        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$). An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}). 
        This is not possible, however, using empirical data. An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        The obvious rule of thumb to reduce uncertainty is ``sample more". Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). Thus, the more we sample, the more zeros will appear in our interaction matrix.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe.

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks. We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed. Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

        \begin{equation}
          \lambda_{MLE} = \frac{k}{n}  .
          \label{theta_MLE}
        \end{equation}

    Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

    To properly interpret $\lambda$, we need to estimate the variance as well as the MLE. The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$. It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).

    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$. This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution. Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:

    \begin{equation}
          \lambda \sim Beta(\alpha,\beta) , \label{prior}
        \end{equation}

        \noindent which has two shape parameters, $\alpha$ and $\beta$.

    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S2}). By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data. When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).

    \subsubsection*{Moments and other properties}
